An Analysis of The Characteristics of the Top Private Equity Firms in the United States That Determine ESG Practices.

### 2024-04-19 paper/paper.qmd
Changes

---
title: "An Analysis of Top Private Equity Firms in the United States' Characteristics That Determine ESG Practices."
author: 
  - Krishiv Jain
thanks: "Code and data are available at: https://github.com/Krishiv-J/ESG-in-Private-Equity"
date: today
date-format: long
abstract: "This paper aims to improve upon the work done and data collected in the ESG in the Top 100 US Private Equity Firms paper, where they analysed different determinants of private equity firm's ESG practices. This is done by fixing certain data inaccuracies, using a different methology to calculate a firm's ESG scores, and considering different variables of interest. The findings reveal that internal rate of return (IRR) and the total number of funds have an impact on ESG score, whereas the number of employees, the fund's size, and the average size of each fund have negligible impact. This research contributes to the understanding the ESG practices of the top private equity firms in the United States."

@@

library(palmerpenguins)
library(here) 
library(arrow)
library(gridExtra)
library(gtsummary)

library(boot)
library(broom.mixed)
library(collapse)
library(dataverse)
library(gutenbergr)
library(janitor)
library(knitr)
library(marginaleffects)
library(modelsummary)
library(rstanarm)
library(tidybayes)
library(tidyverse)

@@

The raw data set used for this paper is obtained from the “ESG in the Top 100 US Private Equity Firms” paper (CITE), which was published in July 2023. The data was collected for the year 2022. This dataset was created by the authors to capture the complex landscape of ESG commitments within private equity firms. Additionally, data was collected from LinkedIn to replace the staff data collected in the original dataset. This is further detailed below. The dataset combines both primary and secondary sources to gather firm-specific variables. The final dataset's sources include Preqin and LinkedIn, with additional insights derived from an analysis of each firm's individual website to assess ESG commitments.

>>>>

---
title: "An Analysis of The Characteristics of the Top Private Equity Firms in the United States That Determine ESG Practices."
author: 
  - Krishiv Jain
thanks: "Code and data are available at: https://github.com/Krishiv-J/ESG-in-Private-Equity"
date: today
date-format: long
abstract: "This paper aims to improve upon the work done and data collected in the ESG in the Top 100 US Private Equity Firms paper, where they analysed different determinants of private equity firm's ESG practices. This is done by fixing certain data inaccuracies, using a different methology to calculate a firm's ESG scores, and considering different variables of interest. The findings reveal that internal rate of return (IRR) and the total number of funds have an impact on ESG score, whereas the number of employees, the fund's size, and the average size of each fund have negligible impact. This research contributes to the understanding the ESG practices of the top private equity firms in the United States."

@@

library(here) 
library(arrow)
library(gridExtra)
library(gtsummary)
library(boot)
library(broom.mixed)
library(collapse)
library(dataverse)
library(gutenbergr)
library(janitor)
library(knitr)
library(marginaleffects)
library(modelsummary)
library(rstanarm)
library(tidybayes)
library(tidyverse)

@@

All data analysis was done through R [@citeR] with the help of the following packages: `tidyverse` [@citetidyverse], `here` [@citehere], `ggplot2` [@citeggplot2], `knitr` [@citeknitr], `rstanarm` [@rstanarm], `dplyr` [@citedplyr], `gridExtra` [@gridExtra], and `janitor` [@citejanitor].

The raw data set used for this paper is obtained from the “ESG in the Top 100 US Private Equity Firms” paper [@paper], which was published in July 2023. The data was collected for the year 2022. This dataset was created by the authors to capture the complex landscape of ESG commitments within private equity firms. Additionally, data was collected from LinkedIn to replace the staff data collected in the original dataset. This is further detailed below. The dataset combines both primary and secondary sources to gather firm-specific variables. The final dataset's sources include Preqin and LinkedIn, with additional insights derived from an analysis of each firm's individual website to assess ESG commitments.
